Industrial, large-scale model predictive control with structured neural networks

### 2020-11-25 paper.tex
submitted the first draft.

\begin{figure*}[!h]
    \centering
	\includegraphics[page=1, width=0.7\textwidth,
		height=0.5\textheight]{cstrs_comparision_plots.pdf}    
        \caption{Transient closed-loop actuator trajectories of the CSTRs with
        flash separator example with the NN and optimal MPC controllers. The
        performance of NN and optimal MPC controllers are almost
        indistinguishable.}   
    \label{fig:cl_cstrs_inputs}
\end{figure*}

\begin{figure*}[!h]
    \centering
	\includegraphics[page=2, width=0.7\textwidth,
		height=0.5\textheight]{cstrs_comparision_plots.pdf} \caption{Transient
		closed-loop controlled measurement trajectories of the CSTRs with flash
		separator example with the NN and optimal MPC controllers. The
		performance of NN and optimal MPC controllers are almost
		indistinguishable.}
		\label{fig:cl_cstrs_outputs}
\end{figure*}

@@

\section*{Acknowledgment}
%The authors acknowledge Professor Stephen J. Wright 
%at the University of Wisconsin, Madison
%for helpful discussions on machine learning topics and providing 
%a detailed feedback on this article.
The funding for this work was provided by the industrial members of the
Texas-Wisconsin-California Control Consortium (TWCCC). The computational
facilities purchased with funds from the National Science Foundation
(CNS-1725797) and administered by the Center for Scientific Computing (CSC) was
used for the simulation studies presented in this article. The CSC is supported
by the California NanoSystems Institute and the Materials Research Science and
Engineering Center (MRSEC; NSF DMR 1720256) at UC Santa Barbara.

>>>>

\begin{figure*}[!h]
    \centering
	\includegraphics[page=1, width=0.7\textwidth,
		height=0.5\textheight]{cstrs_comparision_plots.pdf}    
        \caption{Transient closed-loop actuator trajectories of the CSTRs with
        flash separator example with the NN and optimal MPC controllers. The
        performance of the NN and optimal MPC controllers are almost
        indistinguishable.}   
    \label{fig:cl_cstrs_inputs}
\end{figure*}

\begin{figure*}[!h]
    \centering
	\includegraphics[page=2, width=0.7\textwidth,
		height=0.5\textheight]{cstrs_comparision_plots.pdf} \caption{Transient
		closed-loop controlled measurement trajectories of the CSTRs with flash
		separator example with the NN and optimal MPC controllers. The
		performance of the NN and optimal MPC controllers are almost
		indistinguishable.}
		\label{fig:cl_cstrs_outputs}
\end{figure*}

@@

\section*{Acknowledgment}
The funding for this work was provided by the industrial members of the
Texas-Wisconsin-California Control Consortium (TWCCC). The computational
facilities purchased with funds from the National Science Foundation
(CNS-1725797) and administered by the Center for Scientific Computing (CSC) was
used for the simulation studies presented in this article. The CSC is supported
by the California NanoSystems Institute and the Materials Research Science and
Engineering Center (MRSEC; NSF DMR 1720256) at UC Santa Barbara.
